Space-time adaptivity for parabolic evolution equations

### 2020-05-18 Latex/paper.tex
testy testy

Although the results are measured in a different norm, these results markedly improve
on the recent results by F\"uhrer and Karkulik, \cite[Ex.~5.2.1]{Fuhrer2019}, where an
adaptive rate of $\tfrac{1}{2}$ was observed for the time-slice error and $\tfrac{1}{3}$
for the primary norm\jw{kunnen we *iets* van een vergelijking maken met onze oplossing? We zouden natuurlijk $||u - u^{\udelta \delta}||_Y$ kunnen uitrekenen maar dat is nog niet zo 1-2-3 gedaan, ik denk via
\[
  ||u - u^{\udelta \delta}||_Y^2 = ||u||_Y - 2\la u, u^{\udelta \delta} \ra_Y + \mathbf u^\top \mathbf A_s^\delta \mathbf u
\]
moet het wel lukken, maar is niet super easy-peasy om die inproducten uit te rekenen. Of evt
\[
  \eta_{\text{FK19}} := \|\partial_t u^{\udelta \delta} - \div \nabla u^{\udelta \delta} - g\|_{I \times \Omega}^2 + \|u_0 - \gamma_0 u^{\udelta \delta}\|_{L_2(\Omega)}
\]}
\begin{figure}
  \includegraphics[width=0.5\linewidth]{smooth_adaptive_errors}
  \caption{Error progression of $e^\delta := u - u^{\underline{\delta}\delta}$ as
  a function of $\dim X^\delta$ for adaptive and full grid refinement.\jw{excuse the terrible graph}}
  \label{fig:smooth}
\end{figure}

\subsection{First singular solution}
Selecting the L-shaped domain $\Omega := [-1,1]^2 \setminus [0,1]^2$ with data
$u_0 \equiv 0$ and $g(x,y) := \bbone_{{x^2 + y^2 \leq 1/4}}(x,y)$, the true
solution is unknown in closed form but known to be singular in the re-entrant
corner.\jw{hier wil ik een citatie of *iets* anders} Figure~\ref{fig:cylinder}
shows the error progression

\begin{itemize}
  \item Adaptive vs full vs sparse grid
  \item Misschien de spatial meshes voor wat verschillende $\lambda$, of sowieso
    tellen hoeveel $\lambda$'s er zijn in dit geval? lijkt veel op de numres van FK19
\end{itemize}
\begin{figure}
  \includegraphics[width=0.5\linewidth]{cylinder_adaptive_errors}
  \caption{Error progression of $e^\delta := u - u^{\underline{\delta}\delta}$ as
  a function of $\dim X^\delta$ for adaptive and full grid refinement.\jw{excuse the terrible graph}}
  \label{fig:cylinder}
\end{figure}

@@

\begin{itemize}
  \item Adaptive vs full vs sparse grid
  \item Memory en time graphs
\end{itemize}
\begin{figure}
  \includegraphics[width=0.5\linewidth]{singular_adaptive_errors}
  \caption{Error progression of $e^\delta := u - u^{\underline{\delta}\delta}$ as
  a function of $\dim X^\delta$ for adaptive and full grid refinement.\jw{excuse the terrible graph}}
  \label{fig:singular}
\end{figure}

>>>>

Although the results are measured in a different norm, these results markedly improve
on the recent results by F\"uhrer and Karkulik, \cite[Ex.~5.2.1]{Fuhrer2019}, where an
adaptive rate of $\tfrac{1}{2}$ was observed for the time-slice error and $\tfrac{1}{3}$
for the primary norm\jw{kunnen we *iets* van een vergelijking maken met onze oplossing? We zouden natuurlijk $||u - u^{\udelta \delta}||_Y$ kunnen uitrekenen maar dat is nog niet zo 1-2-3 gedaan, ik denk via
\[
  ||u - u^{\udelta \delta}||_Y^2 = ||u||_Y - 2\la u, u^{\udelta \delta} \ra_Y + \mathbf u^\top \mathbf A_s^\delta \mathbf u
\]
moet het wel lukken, maar is niet super easy-peasy om die inproducten uit te rekenen. Of evt
\[
  \eta_{\text{FK19}} := \|\partial_t u^{\udelta \delta} - \div \nabla u^{\udelta \delta} - g\|_{I \times \Omega}^2 + \|u_0 - \gamma_0 u^{\udelta \delta}\|_{L_2(\Omega)}
\]}
\begin{figure}
  \includegraphics[width=0.5\linewidth]{smooth_adaptive_errors}
  \caption{Error progression of $e^\delta := u - u^{\underline{\delta}\delta}$ for the smooth problem as
  a function of $\dim X^\delta$ for adaptive and full grid refinement.\jw{excuse the terrible graph}}
  \label{fig:smooth}
\end{figure}

\subsection{First singular solution}
Selecting the L-shaped domain $\Omega := [-1,1]^2 \setminus [0,1]^2$ with data
$u_0 \equiv 0$ and $g(x,y) := \bbone_{{x^2 + y^2 \leq 1/4}}(x,y)$, the true
solution is unknown in closed form but known to be singular in the re-entrant
corner.\jw{is het wel singulier? of alleen minder regulier? hier wil ik een citatie of *iets* anders} Figure~\ref{fig:cylinder}
shows the error progression

\begin{itemize}
  \item Adaptive vs full vs sparse grid
  \item Misschien de spatial meshes voor wat verschillende $\lambda$, of sowieso
    tellen hoeveel $\lambda$'s er zijn in dit geval? lijkt veel op de numres van FK19
\end{itemize}
\begin{figure}
  \includegraphics[width=0.5\linewidth]{cylinder_adaptive_errors}
  \caption{Error progression of $e^\delta := u - u^{\underline{\delta}\delta}$ for the cylinder problem as
  a function of $\dim X^\delta$ for adaptive and full grid refinement.\jw{excuse the terrible graph}}
  \label{fig:cylinder}
\end{figure}

@@

\begin{itemize}
  \item Adaptive vs full vs sparse grid
  \item Memory en time graphs
\end{itemize}
\begin{figure}
  \includegraphics[width=0.5\linewidth]{singular_adaptive_errors}
  \caption{Error progression of $e^\delta := u - u^{\underline{\delta}\delta}$ for the singular problem as
  a function of $\dim X^\delta$ for adaptive and full grid refinement.\jw{excuse the terrible graph}}
  \label{fig:singular}
\end{figure}
